Adopting agile in the large: motivations, success factors and challenges

### 2014-04-28 journal/article.tex
Leadership challenges in change

It was quite common that organizations sought to combine agile methods.
Especially Scrum, XP, and Lean software development were used together. In
addition, many cases mentinoed use of XP practices without explicitly stating XP
as the process being used (such as test driven development and continuous
integration). Combining and customizing agile practices was also evident in that
many organizations viewed the agile method as continuously evolving.
Organizations evolved the agile methods for instance through retrospectives and
continuous improvement.

@@

\subsubsection{Challenges caused by management of the transformation}

@@

Organizations had bad experiences with prescribing how to carry out Scrum
practices. For instance, doing agile based on checklists would not work [P41].
Benefield described that it was challenging to find a balance between
independence for teams to choose their way and diluting the value and structure
of Scrum [P6]. Giving room for team autonomy was seen

>>>>

It was quite common that organizations sought to combine agile methods.
Especially Scrum, XP, and Lean software development were used together. In
addition, many cases mentioned use of XP practices without explicitly stating XP
as the process being used (such as test driven development and continuous
integration). Combining and customizing agile practices was also evident in that
many organizations viewed the agile method as continuously evolving.
Organizations evolved the agile methods for instance through retrospectives and
continuous improvement.

@@

\subsubsection{Challenges relating to leading the change}

@@

Organizations had bad experiences with prescribing how to carry out Scrum
practices. For instance, doing agile based on checklists would not work [P41].
Benefield described that it was challenging to find a balance between
independence for teams to choose their way and diluting the value and structure
of Scrum [P6]. Giving room for team autonomy is one of the critical facets of
agile, but it must be ensured that teams do not discard practices that add value
and structure.

Another issue that should be avoided is overenthusiasm towards agile methods.
In several cases there was mentionings about change leaders or teams becoming
agile zealots. For instance, Evans describes how some members of the agile
community were becoming too evangelic, which made people take sides for or
against agile development [12]. In another case team members started out with an
overly eager attitude, but when agile did not deliver improvements quickly the
interest faded and started to go back to the old process [P20]. Attempting to
implement agile too strictly may cause conflicts, and especially in a large
organization the change leaders need to maintain a collaborative attitude
towards various groups in the surrounding organization [P6]. Introducing agile
methods does not guarantee success, and therefore they should not be followed
blindly [P4].

In one case a passive-aggressive organization culture was described as a
challenge. Ranganath describes how people did not speak their minds in meetings,
thus creating a false sense of agreement when talking about how the organization
should develop. Because of this resistance and concerns were left growing, and
acted against achieving a successful transformation. To to avoid these issues
change leaders worked with team members on an individual level to win confidence 
and make their voices heard [P40].

\subsubsection{Challenges in managing the changing organization}
